Back-integration likelihood

### 2013-10-14 text/notes/likelihood.tex
updated note on likelihood

\begin{align}
	p({\bf D}_i, {\bf x}_i^{(0)} \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i) &= 
	p({\bf D}_i | {\bf x}_i^{(0)}) \mathcal{N}({\bf x}_i(t_i\given {\bf x}_i^{(0)}, \Phi ) \given {\bf x}_p(t_i\given {\bf x}_p^{(0)}, \Phi ), {\bf \Sigma}_p)\\
	p({\bf D}_i \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i) &= \int p({\bf D}_i, {\bf x}_i^{(0)} \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i) \dd {\bf x}_i^{(0)}
\end{align}

\section{Tests}
Try for a single star, relative to a perfectly known progenitor. Increase the observational errors on the star, make sure the likelihood gets broader.

>>>>

I've already implemented the case assuming we have perfect data -- that looks like this:
\begin{align}
	p({\bf x}_i^{(0)} \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i) &= 
        \mathcal{N}({\bf x}_i(t_i\given {\bf x}_i^{(0)}, \Phi ) \given {\bf x}_p(t_i\given {\bf x}_p^{(0)}, \Phi ), {\bf \Sigma}_p)\\
	p({\bf x}_i^{(0)} \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi) &= 
	\int p({\bf x}_i^{(0)} \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i) \dd t_i\\
\end{align}
then if we assume we know the position and shape of the progenitor exactly, it becomes a marginal likelihood I can handle:
\begin{align}
	p({\bf x}_i^{(0)} \given \Phi, t_i) &= 
        \mathcal{N}({\bf x}_i(t_i\given {\bf x}_i^{(0)}, \Phi ) \given {\bf x}_p(t_i\given {\bf x}_p^{(0)}, \Phi ), {\bf \Sigma}_p)\\
	p({\bf x}_i^{(0)} \given \Phi) &= 
	\int p({\bf x}_i^{(0)} \given \Phi, t_i) \dd t_i\\
\end{align}
which, numerically, is just:
\begin{align}
	p({\bf x}_i^{(0)} \given \Phi) &= 
	\sum_k \mathcal{N}({\bf x}_i(t_i\given {\bf x}_i^{(0)}, \Phi ) \given {\bf x}_p(t_i\given {\bf x}_p^{(0)}, \Phi ), {\bf \Sigma}_p) \Delta t_{i,k}\\
\end{align}

Now, I want to include the observational errors directly in this model. I think that looks like this:
\begin{align}
	p({\bf D}_i, {\bf x}_i^{(0)} \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i) &= 
	p({\bf D}_i | {\bf x}_i^{(0)}) \mathcal{N}({\bf x}_i(t_i\given {\bf x}_i^{(0)}, \Phi ) \given {\bf x}_p(t_i\given {\bf x}_p^{(0)}, \Phi ), {\bf \Sigma}_p)\\
	p({\bf D}_i \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i) &= \int p({\bf D}_i, {\bf x}_i^{(0)} \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i)p({\bf D}_i | {\bf x}_i^{(0)}) \dd {\bf x}_i^{(0)}
\end{align}
again, assuming we know the progenitor shape and position today perfectly well, then this is:
\begin{align}
	p({\bf D}_i \given \Phi) &= \iint p({\bf D}_i, {\bf x}_i^{(0)} \given {\bf x}_p^{(0)}, {\bf \Sigma}_p, \Phi, t_i)p({\bf D}_i | {\bf x}_i^{(0)}) \dd {\bf x}_i^{(0)} \dd t_i\\
\end{align}
all along assuming a uniform prior on $t_i$.

But I've totally confused myself on how to implement marginalizing over the error distributions...
